---
title: "Common Distributions"
author: "Yuqian Zhang"
date: "January 17, 2020"
output:
  pdf_document: default
  html_document:
    df_print: paged
  word_document: default
---

For more details, see Chapter 4 of [https://www.openintro.org/book/os/](https://www.openintro.org/book/os/), or on Wikipedia.


### Normal Distribution : $N(\mu,\sigma^2)$
Lots of real-life distributions are nearly normal, because of the Central Limist Theorem. The density plot of a normal distribution is symmetric and bell-shaped.

```{r}
dnorm(0)
x <- seq(-5, 5, by=0.1)
d <- dnorm(x, mean=0, sd=1)
plot(x, d, type="l", font.main=1, cex.main=0.9, main="Probability density function of N(0,1)")

pnorm(0)
x <- seq(-5, 5, by=0.1)
p <- pnorm(x)
plot(x, p, type="l", font.main=1, cex.main=0.9, main="Cumulative distribution function of N(0,1)")

qnorm(0.5)
p <- seq(0, 1, by=0.01)
q <- qnorm(p)
plot(p, q, type="l", font.main=1, cex.main=0.9, main="Quantile function of N(0,1)")

x <- rnorm(1000)
hist(x, font.main=1, cex.main=0.9, main="Histogram of N(0,1)", ylim = c(0, 250))
```

### Chi-squared Distribution: $\chi_k^2$
Sum of square of $k$ independent $N(0,1)$.

```{r}
x <- seq(-1, 10, length.out=1000)
d <- dchisq(x, df=1)
plot(x, d, type="l", font.main=1, cex.main=0.9, main="Probability density function of Chi-squared(1)")

x <- seq(-1, 10, length.out=1000)
p <- pchisq(x, df=1)
plot(x, p, type="l", font.main=1, cex.main=0.9, main="Cumulative distribution function of Chi-squared(1)")

p <- seq(0, 1, by=0.01)
q <- qchisq(p, df=1)
plot(p, q, type="l", font.main=1, cex.main=0.9, main="Quantile function of Chi-squared(1)")

x <- rchisq(1000, df=1)
hist(x, font.main=1, cex.main=0.9, main="Histogram of Chi-squared(1)")
```

### Uniform Distribution (continous): Unif$(a,b)$
Density is a constant on the support $(a,b)$.

```{r}
x <- seq(-1, 2, length.out=1000)
d <- dunif(x, min=0, max=1)
plot(x, d, type="l", font.main=1, cex.main=0.9, main="Probability density function of Unif(0,1)")

x <- seq(-1, 2, length.out=1000)
p <- punif(x)
plot(x, p, type="l", font.main=1, cex.main=0.9, main="Cumulative distribution function of Unif(0,1)")

p <- seq(0, 1, by=0.01)
q <- qunif(p)
plot(p, q, type="l", font.main=1, cex.main=0.9, main="Quantile function of Unif(0,1)")

x <- runif(1000)
hist(x, font.main=1, cex.main=0.9, main="Histogram of Unif(0,1)")
```

### Binomial Distribution: Binomial$(n,p)$
Number of heads in n flips, $p$ is the probability of landing a head. Bernoulli$(p)$ is equivalent to Binomial$(n,p)$.

```{r}
x <- seq(1, 10, by=1)
d <- dbinom(x, size=10, prob=0.5)
plot(x, d, type="b", font.main=1, cex.main=0.9, main="Probability mass function of Binomial(10,0.5)")

x <- seq(-1, 11, length.out=1000)
p <- pbinom(x, size=10, prob=0.5)
plot(x, p, type="l", font.main=1, cex.main=0.9, main="Cumulative distribution function of Binomial(10,0.5)")

p <- seq(0, 1, by=0.001)
q <- qbinom(p, size=10, prob=0.5)
plot(p, q, type="l", font.main=1, cex.main=0.9, main="Quantile function of Binomial(10,0.5)")

x <- rbinom(1000, size=10, prob=0.5)
hist(x, font.main=1, cex.main=0.9, main="Histogram of Binomial(10,0.5)")
```

### Geometric Distribution: Geometric$(p)$
Number of flips untill the first head.

```{r}
x <- seq(1, 10, by=1)
d <- dgeom(x, prob=0.5)
plot(x, d, type="b", font.main=1, cex.main=0.9, main="Probability mass function of Geometric(0.5)")

x <- seq(-1, 11, length.out=1000)
p <- pgeom(x, prob=0.5)
plot(x, p, type="l", font.main=1, cex.main=0.9, main="Cumulative distribution function of Geometric(0.5)")

p <- seq(0, 1, by=0.001)
q <- qgeom(p, prob=0.5)
plot(p, q, type="l", font.main=1, cex.main=0.9, main="Quantile function of Geometric(0.5)")

x <- rgeom(1000, prob=0.5)
hist(x, font.main=1, cex.main=0.9, main="Histogram of Geometric(0.5)")
```

### Poisson Distribution: Poisson$(\lambda)$
Assume a bus comes at a constant rate. Poisson$(\lambda)$ denotes the number of buses appears in 1 hour, if the average (expectation) is $\lambda$.

```{r}
x <- seq(1, 10, by=1)
d <- dpois(x, lambda=4)
plot(x, d, type="b", font.main=1, cex.main=0.9, main="Probability mass function of Poisson(4)")

x <- seq(-1, 11, length.out=1000)
p <- ppois(x, lambda=4)
plot(x, p, type="l", font.main=1, cex.main=0.9, main="Cumulative distribution function of Poisson(4)")

p <- seq(0, 1, by=0.001)
q <- qpois(p, lambda=4)
plot(p, q, type="l", font.main=1, cex.main=0.9, main="Quantile function of Poisson(4)")

x <- rpois(1000, lambda=4)
hist(x, font.main=1, cex.main=0.9, main="Histogram of Poisson(4)")
```

### Exponential Distribution: Exponential$(\lambda)$
Time until the next bus show up.

```{r}
x <- seq(-1, 5, length.out=1000)
d <- dexp(x, rate=4)
plot(x, d, type="l", font.main=1, cex.main=0.9, main="Probability density function of Exponential(4)")

x <- seq(-1, 5, length.out=1000)
p <- pexp(x, rate=4)
plot(x, p, type="l", font.main=1, cex.main=0.9, main="Cumulative distribution function of Exponential(4)")

p <- seq(0, 1, by=0.001)
q <- qexp(p, rate=4)
plot(p, q, type="l", font.main=1, cex.main=0.9, main="Quantile function of Exponential(4)")

x <- rexp(1000, rate=4)
hist(x, font.main=1, cex.main=0.9, main="Histogram of Exponential(4)")
```