---
title: "Week5 discussion"
arthor: "Yuqian Zhang"
date: "2/6/2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# Common Mathematical expressions in Latex (Rmarkdown)
## Mathematical modes
The mass-energy equivalence is described by the famous equation
$$E=mc^2$$
discovered in 1905 by Albert Einstein. 
In natural units ($c$ = 1), the formula expresses the identity
\begin{equation}
E=m
\end{equation}

## Symbols
Greek letters:
$$
\alpha,\beta,\gamma,\rho,\sigma,\delta,\epsilon,...
$$
Binary operators:
$$
+,-,*,/,\times,\cdot,\cup,\cap,...
$$
Relation operators:
$$
<,>,=,\leq,\geq,\neq,\subset,\supset,\subseteq,\supseteq,...
$$
Others:
$$
\int,\sum,\prod
$$

## Subscripts and superscripts
$$
x^a,x^aa,x^{aa},x_n,x_n^2,\int_a^b,\sum_{i\leq10},\prod_{i=1}^{10}
$$
Want more? See https://www.overleaf.com/learn/latex/Mathematical_expressions or google what you want.

# Chunk options in Rmarkdown 
## Hide your code and show your result
```{r chunk1, echo=FALSE}
print("Invisible code!")
```

## Hide your result (show and run your code)
```{r chunk2, echo=TRUE, results="hide"}
x=0
print("Invisible code?")
```

## Show your code (without running your code)
```{r chunk3, echo=TRUE, eval=FALSE}
x=1
```
$$x=`r x`$$

## Append your code
```{r ref.label=c("chunk1","chunk2","chunk3"), echo=TRUE, eval=FALSE}
```
Want more? See https://rstudio.com/wp-content/uploads/2015/03/rmarkdown-reference.pdf

# Delta Method
## Theorem
Suppose we have an asymptotically normal r.v. Y:
$$
\sqrt n(Y_n-\mu)\dot\sim N(0,\sigma^2),
$$
then
$$
\sqrt n[g(Y_n)-g(\mu)]\dot\sim N\left(0,[g'(\mu)]^2\sigma^2\right),
$$
if $g(y)$ is differentiable and $g'(\mu)\neq0$.

## Example
Suppose $\log(\hat\mu)$ is an estimator of $\log(\mu)$ that
$$
\sqrt n[\log(\hat\mu)-\log(\mu)]\dot\sim N(0,\sigma^2).
$$
Hence, we can contruct an asymptotic $95\%$ confidence interval for $\log(\mu)$:
$$
\log(\hat\mu)\pm1.96\sqrt{\frac{\sigma^2}{n}}
$$
How can be obtain an asymptotic confidence interval for $\mu$, instead of $\log(\mu)$?
Let $g(y)=e^y$, then $g'(y)=e^y$. By Delta method,
$$
\sqrt n[g(\log(\hat\mu))-g(\log(\mu))]\dot\sim N\left(0,[g'(\log(\mu))]^2\sigma^2\right),
$$
where $g(\log(\hat\mu))=\hat\mu$, $g(\log(\mu))=g'(\log(\mu))=\mu$. That is,
$$
\sqrt n[\hat\mu-\mu]\dot\sim N\left(0,\mu^2\sigma^2\right).
$$
Therefore, an asymptotic $95\%$ confidence interval for $\mu$ can be obtained as:
$$
\hat\mu\pm1.96\sqrt{\frac{\mu^2\sigma^2}{n}}.
$$


