---
title: "week6 discussion"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Joint probability distribution

Suppose there are $K$ random variables $X_1,\dots,X_K$, the joint cumulative distribution function is
$$
F_{X_1,\dots,X_K}(x_1,\dots,x_K)=P(X_1\leq x_1,\dots,X_K\leq x_K).
$$
When $X_1,\dots,X_K$ are discrete random variables, the joint probability mass function is
$$
p_{X_1,\dots,X_K}(x_1,\dots,x_K)=P(X_1=x_1,\dots,X_K=x_K).
$$
When $X_1,\dots,X_K$ are continuous random variables, the joint probability density function is
$$
f_{X_1,\dots,X_K}(x_1,\dots,x_K)=\frac{\partial^KF_{X_1,\dots,X_K}(x_1,\dots,x_K)}{\partial X_1\dots\partial X_K}.
$$
If $X_1,\dots,X_K$ are mutually independent, then (for continuous case)
\begin{align*}
F_{X_1,\dots,X_K}(x_1,\dots,x_K)=\prod_{k=1}^KF_{X_k}(x_k),\\
f_{X_1,\dots,X_K}(x_1,\dots,x_K)=\prod_{k=1}^Kf_{X_k}(x_k).
\end{align*}

# Covariance matrix

Let $\mathbf{X}=(X_1,\dots,X_K)^\top\in\mathbb R^K$ and $\mathbf{Y}=(Y_1,\dots,Y_L)^\top\in\mathbb R^L$ be two random vectors. The cross-covariance matrix of $\mathbf{X}$ and $\mathbf{Y}$ is defined by
$$
\mathrm{cov}(\mathbf{X},\mathbf{Y})=E[(X-EX)(Y-EY)^\top]=E[XY^\top]-EX\cdot EY^\top\in\mathbb R^{K\times L}.
$$
The covariance matrix of $\mathbf{X}$ (also known as auto-covariance matrix, dispersion matrix, variance matrix, or variance–covariance matrix) is the cross-covariance matrix of $\mathbf{X}$ and $\mathbf{X}$,
$$
\mathrm{cov}(\mathbf{X},\mathbf{X})=E[(X-EX)(X-EX)^\top]=E[XX^\top]-EX\cdot EX^\top\in\mathbb R^{K\times K}.
$$
Properties:
\begin{itemize}
\item $\mathrm{cov}(\mathbf{X},\mathbf{Y})=\mathrm{cov}(\mathbf{Y},\mathbf{X})^\top$.
\item $\mathrm{cov}(\mathbf{X_1}+\mathbf{X_2},\mathbf{Y})=\mathrm{cov}(\mathbf{X_1},\mathbf{Y})+\mathrm{cov}(\mathbf{X_2},\mathbf{Y})$.
\item $\mathrm{cov}(A\mathbf{X}+a,B^\top\mathbf{Y}+b)=A\mathrm{cov}(\mathbf{X},\mathbf{Y})B$.
\end{itemize}

# Logistic regression
Suppose $\mathbf{X}_1,\dots,\mathbf{X}_n\in\mathbb R^K$ are iid random vectors, where $\mathbf{X_i}=(X_{i1},\dots,X_{iK})^\top$. The logistic regression model assumes that, for $i=1,\dots,n$,
\begin{equation}\label{eq1}
\mathrm{logit}(p_i)=\log\left(\frac{p_i}{1-p_i}\right)=\beta_0+\beta_1x_{i1}+\dots+\beta_Kx_{iK},\quad Y_i\sim\mathrm{Bernoulli}(p_i).
\end{equation}
An example:
```{r icu}
#install.packages("aplore3") 
require(aplore3)
data(icu)
summary(icu$sta)
summary(icu$race)
summary(icu$loc)
fit=glm(sta~gender+age+race+loc, family=binomial(), data=icu)
```
Remarks:
\begin{itemize}
\item Be aware of the "sparsity" of your dataset. If the response or the categorical predictors are extremely unbalenced, your results might be problematic.
\item Binary categorical predictors are treated as 0 and 1's, a general categorical predictor with $l$ levels is transformed to $l-1$ indicator variables.
\end{itemize}
```{r icu.summary}
summary(fit)
```
Intepreting your results:

The estimated coefficients $\hat\beta$ is
```{r coef}
fit$coefficients
```
The estimated variance-covariance matrix of $\hat\beta$ is
```{r cov}
summary(fit)$cov.unscaled
```
Assuming the logistic model \eqref{eq1}, the p-values when testing $\beta_k=0$ for each $k\leq K$ are
```{r pval}
summary(fit)$coefficients[,4]
```
Nested models:
```{r anova}
anova(fit, test="LRT")
```
The tests are sequential. First it tests $\beta_\mathrm{gender}=0$ under the model $\mathrm{logit}(p_i)=\beta_0+\beta_\mathrm{gender}x_{i,\mathrm{gender}}$, then it tests $\beta_\mathrm{age}=0$ under the model $\mathrm{logit}(p_i)=\beta_0+\beta_\mathrm{gender}x_{i,\mathrm{gender}}+\beta_\mathrm{age}x_{i,\mathrm{age}}$... Note that the df of race is 2, which means that we are testing $\beta_\mathrm{racewhite}=0$ and $\beta_\mathrm{raceother}=0$ simultaneously.

Anova between two models:
```{r anova2}
fit=glm(sta~gender+age+race+loc, family=binomial(), data=icu)
fit2=glm(sta~gender+age+loc, family=binomial(), data=icu)
anova(fit2,fit,test="LRT")
```

